---
name: Victor Yuan
position: "PhD Candidate"
address: "Genome Sciences and Technology, UBC. Vancouver, Canada"
email: "victor.2wy@gmail.com"
twitter: victor2wy
github: wvictor14
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(rorcid)
library(janitor)
library(lubridate)
library(scholar)

# load data
experience <- read_csv('../data/experience.csv') %>%
  fill(Start, End, What, With, Where, Tag) %>%  
  arrange(desc(Start)) %>% 
  
  # format so that year is shown
  mutate(End = ifelse(End == 'Present', NA, End),
         When = gsub('NA', 'Present', paste0(year(Start), '--', year(End)))) 

awards <- read_csv('../data/awards.csv') %>%
  mutate(When = gsub('--NA', '', paste0(year(Start), '--', year(End))))

bibliography <- bibliography_entries('../data/citations.bib')

# for debugging
options(tinytex.verbose = TRUE)

```

# Skills

## **Dry**

* DNA methylation microarray, RNA expression (sequencing/microarray), Genotyping microarray analysis
* Supervised machine learning, Regression analysis, Data cleaning, Data visualization
* R, Bash
* `Tidyverse`, `Rmarkdown`, `ggplot2`, `Git`

## **Wet**

* DNA extraction, Gel electrophoresis, PCR, primer design
* Genotyping, Sequencing, Microarray prep

# Education

```{r education}
edu <- orcid_educations("0000-0002-3394-998X")

# process/clean education data
edu <- edu$`0000-0002-3394-998X`$`affiliation-group`$summaries %>%
  map(as_tibble) %>%
  bind_rows() %>%
  clean_names %>%
  rename_all(~gsub('education_summary_', '', .)) %>%
  select(organization_name:organization_address_country, department_name, 
         role_title, contains('start'), contains('end'), -organization_disambiguated_organization) %>%
  mutate(
         #start = paste(start_date_year_value, start_date_day_value, start_date_month_value, sep = '-'),
         #end = ifelse(is.na(end_date_year_value), 'Present', 
         #              paste(end_date_year_value, end_date_day_value, end_date_month_value, sep = '-')),
    
    # created detailed entries information
    what = paste0(role_title, ', ', department_name),
    when = gsub('NA', 'Present', paste0(start_date_year_value, ' -- ', end_date_year_value)),
    with = organization_name,
    where = organization_address_city) 

# display education
edu %>%
  detailed_entries(
    with =  paste0(role_title, ', ', department_name),
    what = organization_name,
    when = when,
  )
```

# Research

```{r}
experience %>%
  filter(Tag == 'Research') %>%
  detailed_entries(
    with = What,
    when = When,
    what = With,
    where = Where,
    why = Why
  )
```

# Teaching

```{r}
experience %>%
  filter(Tag == 'Teaching') %>%
  detailed_entries(
    with = What,
    what = Where,
    when = When,
    why = Why
  )
```

# Awards

```{r}
awards %>%
  brief_entries(
    what = paste0(What, ', ', With),
    when = When
  )
```

# Publications

```{r eval = T}
# google scholar method
#get_publications('k_dOrEoAAAAJ') %>% as_tibble

bibliography %>%
  slice(nrow(.):1)
```



